Курсовая работа по теме \\ \Huge{«Методы оптимизации»}

### 2008-12-18 paper.tex
Separate section on convexity
New commands for algorithm names
New theorem environments using small caps
Additions about on Rosenbrock function
Bug fixed
New style added
New acronym commands
New style
Removed styles
Using subfigure package
Hanging captions
Different style for subfigures
Using wrapfigure
Set grids for all plots
Added pgfplotstable package to preamble
8 copies is sufficient
Better \paragraph
Using cancel
Forgot to add acronym definition
Added source code listings
Fixed regression typos, added doc info, listings options changed

\usepackage[auto]{contour}
\contourlength{1pt}

@@

\usepackage{pgfplots}
\usetikzlibrary{patterns,arrows}
\pgfplotsset{every axis/.append style={enlargelimits=0.05}}
\pgfplotsset{every axis grid/.append style={densely dotted}}
\pgfplotsset{every tick/.append style={black}}

@@

@@

% Custom commands
\newcommand{\program}[1]{{\tt #1}}
\newcommand{\La}{\mathcal{L}}
\newcommand{\neword}{\emph}
\newcommand{\pardiff}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\dpardiff}[3]{\frac{\partial^2{#1}}{\partial{#2}\partial{#3}}}
\newcommand{\abs}[1]{\left \lvert{#1}\right \rvert}
\newcommand{\norm}[1]{\left \lVert{#1}\right \rVert}
\newcommand{\set}[1]{\mathbb{#1}}
\newcommand{\mul}{\cdot}
\newcommand{\scalmult}[1]{{\left \langle #1 \right \rangle}}
% Minus for matrices
\newcommand{\mm}[1]{\hspace{-7.5pt}{-{#1}}}
\newcommand{\phm}{\phantom{-}}
\DeclareMathOperator{\rank}{rg}
\DeclareMathOperator{\extr}{extr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Sp}{Sp}

% Theorems, remarks and definition all share the same numbering
% sequence, which is also subordinate to sections
\newtheorem{thm}[]{Теорема}
\numberwithin{thm}{section}
\theoremstyle{remark}
\newtheorem{rem}[thm]{Замечание}
\theoremstyle{definition}
\newtheorem{dfn}[thm]{Определение}

@@

@@

\clearpage
\appendix
\bibliographystyle{gost71s}
\bibliography{paper}

>>>>

% Contours for plot labels
\usepackage[auto]{contour}
\contourlength{1pt}
\contournumber{8}

@@

% PGF/TikZ and pgfplots
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{pgfplots}
\usetikzlibrary{patterns,arrows}
\pgfplotsset{every axis/.append style={enlargelimits=0.05}}
\pgfplotsset{every axis/.append style={grid=both}}
\pgfplotsset{every axis grid/.append style={densely dotted}}
\pgfplotsset{every tick/.append style={black}}

% Tables
\usepackage{pgfplotstable}
\pgfkeys{/pgf/number format/.cd, set thousands separator={\,}}
\usepackage{booktabs}

% Listings
\usepackage{listings}
\lstdefinelanguage[plt]{Scheme}
        {morekeywords={define,let,map,lambda,if,cond,or,and,else},
         morecomment=[l]{;},
         morestring=[b]{"}}
\lstset{mathescape=true}
\lstset{language=[plt]Scheme}
\lstset{basicstyle=\footnotesize\sffamily}
\lstset{breakautoindent=true}

@@

% Better \paragraph command with small caps and line skip
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{0em}{-\baselineskip}{0.25\baselineskip}{\scshape}}
\makeatother

\usepackage{wrapfig}

% Subfigures
\usepackage[tight]{subfigure}
\renewcommand{\thesubfigure}{(\asbuk{subfigure})~}

% Nice captions
\usepackage[format=hang]{caption}

@@

% Dashing out
\usepackage{cancel}

% Custom commands
\newcommand{\program}[1]{{\sf #1}}
\newcommand{\filename}[1]{{\tt #1}}
\newcommand{\relch}{\textsc{relch}}
\newcommand{\gdrelch}{\textsc{gdrelch}}
\newcommand{\xrelch}{\textsc{xrelch2}}
\newcommand{\gd}{\textsc{пгс}}
\newcommand{\rgd}{\textsc{пгс}$_2$}
\newcommand{\La}{\mathcal{L}}
\newcommand{\neword}{\emph}
\newcommand{\pardiff}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\dpardiff}[3]{\frac{\partial^2{#1}}{\partial{#2}\partial{#3}}}
\newcommand{\abs}[1]{\left \lvert{#1}\right \rvert}
\newcommand{\norm}[1]{\left \lVert{#1}\right \rVert}
\newcommand{\set}[1]{\mathbb{#1}}
\newcommand{\mul}{\cdot}
\newcommand{\scalmult}[1]{{\left \langle #1 \right \rangle}}
\newcommand{\at}[2]{\left. {#1}\right\vert_{#2}}
% Minus for matrices
\newcommand{\mm}[1]{\hspace{-7.5pt}{-{#1}}}
\newcommand{\phm}{\phantom{-}}
\DeclareMathOperator{\rank}{rg}
\DeclareMathOperator{\extr}{extr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Sp}{Sp}

% Theorems, remarks and definition all share the same numbering
% sequence, which is also subordinate to sections
\newtheoremstyle{ruthm}{3pt}{3pt}{\itshape}{}{\scshape}{.}{.5em}{}
\newtheoremstyle{rudfn}{3pt}{3pt}{}{}{\scshape}{.}{.5em}{}
\newtheoremstyle{rurem}{}{}{}{}{\scshape}{.}{.5em}{}

\theoremstyle{ruthm}
\newtheorem{thm}[]{Теорема}
\numberwithin{thm}{section}

\theoremstyle{rurem}
\newtheorem{rem}[thm]{Замечание}

\theoremstyle{rudfn}
\newtheorem{dfn}[thm]{Определение}

@@

\clearpage
\input{general.tex}

@@

\clearpage
\appendix
\section{Исходные тексты}
\label{sec:sources}

\subsection{Общая схема градиентных методов}
\input{gradient-methods.ss-full-listing.tex}

\subsection{Алгоритмы \relch{}, \gdrelch{}, \gd{} и \rgd{}}
\input{relch.ss-full-listing.tex}

\section{Информация о документе}

Данный документ был подготовлен с использованием \LaTeX{}. В качестве
реализации языка Scheme использовалась \program{PLT Scheme}.
Иллюстрации созданы с помощью пакета \program{pgfplots} и
\program{gnuplot}.

Автоматизация процесса сборки обеспечивалась утилитами
\program{GNU Make} и \program{texdepend}.

Представленная работа выполнена в рамках программы пятого семестра
обучения по специальности «Вычислительная математика и математическая
физика» в МГТУ им. Н. Э. Баумана.

Дата компиляции настоящего документа: \today

\bibliographystyle{gost71s}
\bibliography{paper}
